---
title: "Import raw data"
format: gfm
---

## Data source

Data is downloaded from https://ftp.cdc.gov/pub/Health_Statistics/NCHS/Datasets/NSFG/ on 8/14/2024 including:

- 2011_2019_FemaleWgtData.dat
- 2017_2019_FemPregData.dat

National Center for Health Statistics (NCHS). (2020). 2017-2019 National Survey of
Family Growth Public-Use Data and Documentation. Hyattsville, MD: CDC National
Center for Health Statistics. Retrieved from
http://www.cdc.gov/nchs/nsfg/nsfg_2017_2019_puf.htm.

## Import data

```{r}
#| label: package-load

library(tidyverse)
library(tidylog)
```


```{r}
#| label: import-wts

surv_wt_in <- read_fwf(
  here::here("raw-data", "2011_2019_FemaleWgtData.dat"),
  col_positions = fwf_positions(
    start=c(1, 6, 22, 38, 54, 70, 86), 
    end=c(5, 21, 37, 53, 69, 85, 101),
    col_names=c("CASEID", "WGT2011_2015", "WGT2013_2017", "WGT2015_2019", "WGT2011_2017", "WGT2013_2019", "WGT2011_2019")),
  col_types="n")

summary(surv_wt_in)
glimpse(surv_wt_in)
```

```{r}
#| label: import-preg-dat

preg_dat_in <- read_fwf(
  here::here("raw-data", "2017_2019_FemPregData.dat"),
  col_positions = fwf_positions(
    start=c(1, 6, 8, 9, 10, 45, 102, 103, 105, 106, 138, 221, 222, 248), 
    end=  c(5, 7, 8, 9, 10, 45, 102, 103, 105, 107, 139, 221, 224, 251),
    col_names=c("CASEID", "PREGORDR", "MOSCURRP", "PREGEND1", "PREGEND2", "NBRNLV_S", "GEST_LB", "GEST_OTHR", "OUTCOME", "BIRTHORD", "AGER", "SECU", "SEST", "INTVWYEAR")),
  col_types="n")

summary(preg_dat_in)
glimpse(preg_dat_in)
```

```{r}
#| label: merge-data

dat_tog <- preg_dat_in %>%
  left_join(select(surv_wt_in, CASEID, WGT2011_2019), by="CASEID")

nrow(preg_dat_in)
nrow(dat_tog)
```

```{r}
#| label: mismatch-inv

dat_tog %>% filter(is.na(WGT2011_2019)) %>% summary()
```

Those age 45-50 do not have weights so the whole set has a consistent age. This older group was only added in later years.


```{r}
#| label: adj-wt

dat_tog_wt <- dat_tog %>%
  mutate(
    WGT2011_2019=replace_na(WGT2011_2019, 0)
  )
```


```{r}
#| label: save-data

write_rds(dat_tog_wt, here::here("Data", "d01_preg_dat.rds"))
```

